\documentclass[10pt,a4paper]{moderncv}
\moderncvtheme[grey]{classic}
\usepackage[utf8]{inputenc}

\usepackage[scale=0.9]{geometry}
\recomputelengths 


\newcommand{\rdated}[4]{
  \cvline{#1}{\textbf{#2}, \textit{#3} \hfill #4}
}

\firstname{Joshua}
\familyname{Davis}
\mobile{1-646-266-7445}
\email{sivad77@gmail.com}

\begin{document}
\maketitle

\section{PERSONAL INFORMATION}
\cvline{Citizenship}{A dual American and Australian citizen.}

\section{EDUCATION}

\rdated{02/04 - 06/08}{Bachelor of Science}{Monash University}{Melbourne, Victoria, Australia}
\cvitem{Majors}{Computer Science and Mathematics}
\cvitem{Coursework}{Included: data structures and algorithms;
programming languages and implementation; computer graphics; image processing;
software engineering; parallel computing; partial differential equations;
computational mathematics; atmospheric science; biology; histology.}
\cvitem{Awards}{Letter of excellence for highest grade in image processing (grade 93\%).}

\subsection{}
\rdated{10/03}{Victorian Certificate of Education}{Caulfield Grammar School}{Melbourne, Victoria, Australia}
\cvitem{Awards}{Received the ``Daryl Rosenfield Memorial Prize" for Information Technology in year 12, Caulfield Grammar School Certificate of Excellence and Emblem for $2^{nd}$ VIII Rowing.}

\section{EMPLOYMENT HISTORY}

\rdated{06/08 - 01/11}{Software Developer}{Integrated Application Development}{Melbourne, Victoria, Australia}
\cvitem{Technologies}{Delphi, Firebird, Linux, KVM, QATime and Git}
\cvitem{Description}{An Australian firm that develops portfolio management
software for a British client with over 10 billion pounds of funds under administration.}
\cvitem{Role}{Tools and framework teams, focusing on clean, simple, efficient code:
\begin{itemize}
\item Narrowed the database object framework API without lose of functionality (lead to easier maintenance).
\item Introduced compression into the logging framework resulted in a 10x space saving for log files.
\item Simplified the log viewer with over 120x speedup (from over 10 minutes to seconds to view large log files).
\item Ensured all bugs were allocated before the start of the work day (followed from log framework improvements).
\item Disentangled legacy code (FoxPro) into a straightforward framework.
\item Improved the robustness of the unit-test framework (inculded removing GUI and popup windows, added parallelism to framework and crash protection with sandboxing).
\item Decreased the overnight build time to under an hour (included running all unit-tests) which previously never reliably completed (utilized parallelism which lead to the dramatic speedup).
\item Lead the adoption of Git which included developing a work flow, migrated 10 years of development history from Starteam, set up the infrastructure and initial staff training.
\item Encouraged developers to employ test driven development coupled with writing clear, simple, efficient code.
\end{itemize}
}

\subsection{}
\rdated{01/04 - 10/07}{Laborer}{Fendon Fences}{Melbourne, Victoria, Australia}
\cvitem{Description}{Worked 30 hours a week during university.}

\newpage

\section{TECHNICAL SKILLS}

\cvitem{Principles}{Test Driven Development, Continuous Integration, Object Oriented Design and Project Tracking (JIRA).}
\cvitem{Platforms}{Proficient in Linux (all flavors on x86) and Windows (Delphi IDE and Visual Studio).\newline{} Knowledgeable in Mac OSX (XCode) and *BSD.}
\cvitem{Languages}{Proficient in C, Delphi, Python, Perl and Bash.\newline{} Knowledgeable in Java, Javascript, C++, Ruby, Go, SML, PHP and SQL (Firebird dialect)}
\cvitem{Web}{Knowledgeable in XML, JSON, CSS and XHTML.}
\cvitem{Tools}{Proficient in git, StarTeam, QATime, gcc, vim, make, \LaTeX, Firebird and general unix command-line tools.\newline{} Knowledgeable in KVM, gprof, Samba, rsync, cron, NFS, MySQL and GNUPlot.}
\cvitem{Libraries}{Knowledgeable in GTK, clutter, zLib, elightenment and OpenGL.}
\cvitem{Mathematics}{Knowledgeable in numerical computing, ordinarily and partial differential equations and abstract algebra.}

\section{GENERAL SKILLS}

\cvitem{}{
\begin{itemize}
\item I love to learn!
\item Strong verbal and written communication skills.
\item Excellent troubleshooting and debugging skills.
\item Fast learner.
\item Flexible.
\end{itemize}
}
 
\section{INTERESTS}
\cvitem{}{Board games, camping, peanut butter chocolate chip cookies, travel, cycling, running, weight training, fishing, and open source software.}







\end{document}
